### 2015-07-06 narrative/management.tex
getting changes for the evaluatoin

\section*{Management}
\label{sec:management}

@@

Dr. Klasky will oversee the outcome of this project,  Dr. Abbasi (ORNL) will lead the Application Interface area, and Dr. Lofstead
will lead the Storage System. This project is focused on the integration of application aware-middleware which communications to the storage system,
and each of these leaders have a strong track record of tight-collaboration, both working with Dr. Klasky for their Ph.D. at the Georgia
Institute of Technology.  Our structure includes an area lead for each major research area plus
an integration lead responsible for coordinating periodic integration tests. The area leads plus the project PIs
form the management team, which will meet weekly to review progress and revise plans as needed.
We will also have a {\bf Science Advisory Board} consisting of one application Scientist, Dr. C. S. Chang (PPPL), one storage system expert from the 
OLCF, Dr. Vazhkudai (ORNL) who we will advice us yearly on our project goals and outcomes and make adjustments accordingly. We will also have our
lead Math Lead, Dr. Ainsworth, to work with the applied mathematics community to ensure that the hierarchical decomposition of data will work in theory
for current and next generation exascale simulations.

We will conduct six-monthly {\bf integration fests}  to validate our ability to combine models, apply
combined models to real problems, and cope with the challenges of real data. We apply this approach routinely
in other projects and find that it helps to focus effort and identify problems early. The tasks of defining,
scheduling, and running critical post hoc reviews of integration tests will be coordinated by the Integration Lead, Dr. Parashar. 
These meetings will bring all hands together at least once a year.

We will monitor and report {\bf success metrics} including: 
research publications;
our ability to predict and explain performance of I/O workloads on the current machines., in different environments;
our ability to reduce data and charcterize data from an object into multiple bins, 
our ability to integrate our routines into the Sirocco file system and test the feasibily on current and next generation LCF systems, and
how tools lead to workflow performance improvements, for both reading and writing data from our exemplar applications which we will test.

\begin{table}[t]
\caption{S2E2 Integration Tests. We list for each the technology area involved and new technologies expected.}
\centering \footnotesize
\vspace{2ex}
\label{tab:ifests}
%\begin{tabular}{| p{2cm} | p{2.5cm} | p{5cm} | p{5cm} | }
\begin{tabular}{| l | l |l |l |} 
\hline
{\bf \#} &  {\bf Focus} & {\bf New technologies to be introduced} \\\hline
1 & TBD			 & TBD\ \ \\
2 &TBD & TBD\\
3 & TBD         & TBD \\
4 & TBD                                    & TBD  \\
5 & TBD                                    & TBD \\
6 & TBD                                    & TBD  \\\hline
\end{tabular}
\vspace{-8ex}
\end{table}

>>>>

\section{Management}
\label{sec:management}

@@

Dr. Klasky will oversee the outcome of this project,  Dr. Abbasi (ORNL) will lead the Application Interface area, and Dr. Lofstead
will lead the Storage System. This project is focused on the tight integration of application aware-middleware and a storage system backend.
Our team has a strong track record of tight-collaboration, with both Drs. Abbasi and Lofstead both working with Dr. Klasky for their Ph.D. at the Georgia
Institute of Technology.  Our structure includes an area lead for each major research area plus
an integration lead responsible for coordinating periodic integration tests. The area leads plus the project PIs
form the management team, which will meet weekly to review progress and revise plans as needed.
We will also have a {\bf Science Advisory Board} consisting of one application Scientist, Dr. C. S. Chang (PPPL), one storage system expert from the 
OLCF, Dr. Vazhkudai (ORNL) who we will advice us yearly on our project goals and outcomes and make adjustments accordingly. We will also have our
lead Math Lead, Dr. Ainsworth, to work with the applied mathematics community to ensure that the hierarchical decomposition of data will work in theory
for current and next generation exascale simulations.

We will conduct six-monthly {\bf integration tests}  to validate our ability to combine models, apply
combined models to real problems, and cope with the challenges of real data. We apply this approach routinely
in other projects and find that it helps to focus effort and identify problems early. The tasks of defining,
scheduling, and running critical post hoc reviews of integration tests will be coordinated by the Integration Lead, Dr. Parashar. 
These meetings will bring all hands together at least once a year.

We will monitor and report {\bf success metrics} including: 
research publications;
our ability to predict and explain performance of I/O workloads on the current machines., in different environments;
our ability to reduce data and characterize data from an object into multiple bins, 
our ability to integrate our routines into the Sirocco file system and test the feasibily on current and next generation LCF systems, and
how tools lead to workflow performance improvements, for both reading and writing data from our exemplar applications which we will test.

### 2015-07-06 narrative/proposed-work.tex
getting changes for the evaluatoin

We propose to overcome these challenges by pioneering a new {\bf
knowledge-centric approach} to a dynamic storage system and I/O layer which
takes into account user prioritization and utility to optimize the SSIO layer.
The approach is based on three underlying principles:

\underline{Principle 1:} A knowledge-centric system , let user knowledge  to
define data policies. Today Storage System and I/O layers are written in a
stove-pipe fashion, and quite often do not allow optimizations to take place.
We propose to re-design the layer in a highly integrated fashion where user
will place their intentions into the system and actions will dynamically and
statically take place to optimize for both the system and for individual
requests.

\underline{Principle 2}: Predictable Performance in the SSIO layer needs to be
established so more science can be done on the exascale systems. Without
predictable performance, the I/O layer performance must be guessed by the
users, which quite often mean that science is not performed well.

\underline{Principle 3:} In a data-centric SSIO system, we need user goals to
define the data policies. We introduce data-driven SSIO optimizations by
enabling users to define data manipulations (re-organizations) at a high level
and then we express policy goals by associating intentions (hints) with data;
e.g. ``this data at this level should be accessible within 100 seconds in the
next three months.'' These high level specifications of desired results will be
used in our system for data migration and eviction policies.

>>>>

We propose to overcome these challenges by pioneering a new {\bf
knowledge-centric approach} to a dynamic storage system and I/O layer which
takes into account user prioritization and utility to optimize the SSIO layer.
The approach is based on two underlying principles:

\underline{Principle 1:} {\bf A knowledge-centric system design}, let user knowledge  to
define data policies. Today Storage System and I/O layers are written in a
stove-pipe fashion, and quite often do not allow optimizations to take place.
We propose to re-design the layer in a highly integrated fashion where user
will place their intentions into the system and actions will dynamically and
statically take place to optimize for both the system and for individual
requests.

\underline{Principle 2}: {\bf Predictable performance and quality of data in the SSIO layer} needs to be
established so more science can be done on the exascale systems. Without
predictable performance, the I/O layer performance must be guessed by the
users, which quite often mean that science is not performed well.

%\underline{Principle 3:} {\bf Users goals define data policies} In a data-centric SSIO system. 
%We introduce data-driven SSIO optimizations by
%enabling users to define data manipulations (re-organizations) at a high level
%and then we express policy goals by associating intentions (hints) with data;
%e.g. ``this data at this level should be accessible within 100 seconds in the
%next three months.'' These high level specifications of desired results will be
%used in our system for data migration and eviction policies.
